### 2014-11-12 abstract.tex
Add facts derived

Declarative programming has been hailed as a promising approach to parallel
programming since it hides the implementation details of parallelism away from the
programmer. However, its advantage has also been its downfall
as it leaves the programmer with no straightforward way
to optimize programs for performance.
In this paper, we introduce Coordinated Linear Meld, a concurrent forward-chaining linear logic programming
language, with a declarative way to coordinate the execution of the program
allowing the programmer to change
computation scheduling and data layout. Our approach allows the programmer to
write declarative parallel programs and then optionally use coordination 
to fine tune programs, while keeping the program fully declarative and amenable
to correctness proofs.

>>>>

Declarative programming has been hailed as a promising approach to parallel
programming since it hides the implementation details of parallelism away from the
programmer. However, its advantage has also been its downfall
as it leaves the programmer with no straightforward way
to optimize programs for performance.
In this paper, we introduce Coordinated Linear Meld, a concurrent forward-chaining linear logic programming
language, with a declarative way to coordinate the execution of the program
allowing the programmer to change
computation scheduling and data layout. Our approach allows the programmer to
write declarative parallel programs and then optionally use coordination 
to fine tune programs, while keeping the program fully declarative and easy to
reason about.

### 2014-11-12 conclusions.tex
Add facts derived

We have presented a novel way of adding coordination to a declarative language without
changing the nature of the language or introducing non-declarative constructs. We
took advantage of the fact that CLM uses linear logic, which allows us to derive
coordination facts that can be deleted in order to perform actions in the underlying
runtime system. In the other hand, sensing facts allow the programmer to reason
about locality and scheduling of computation in a data-driven fashion.
Even though the programs are optimized, the proofs of correctness for CLM
programs remain simple since coordination does not change the language.

We would like to explore CLM's coordination principles in distributed systems,
where data locality is far more important than in shared memory systems.
Furthermore, we think that other declarative paradigms would benefit
from giving programmers the freedom to fine-tune their programs while keeping
the program declarative and easy to reason about.

>>>>

We have presented a novel way of adding coordination to a declarative language without
changing the nature of the language or introducing non-declarative constructs. We
took advantage of the fact that CLM uses linear logic, which allows us to derive
coordination facts that can be deleted in order to perform actions in the underlying
runtime system. In the other hand, sensing facts allow the programmer to reason
about data locality and scheduling of computation in a data-driven fashion.
Even though the programs are optimized, programs remain declarative and proving
interesting properties of the programs remains simple because it is possible to
reason about the logical rules that drive coordination.

We would like to explore CLM's coordination principles in distributed systems,
where data locality is far more important than in shared memory systems.
Furthermore, we think that other declarative paradigms such as functional
programming would benefit from giving programmers the freedom to fine-tune their
programs.
